### 2015-02-18 src/4_OnlineLearning.tex
Learning theory

There are three types of ML classified depending on the nature of the learning input or output available to a learning system.
\begin{description}
\item[supervised learning]  the input data is a tuple which contains the example input and its desired outputs (also called labels). The list of tuples is called the training set. The concept of supervised learning comes from the supervisor, acting as a teacher in the learning process. The goal is to learn a general rule that maps inputs to outputs optimising a target function. There are two related problem types in supervised learning: classification and regression problems \cite{bishop2006}. Its two mainstream approaches are: support vector machines (SVMs) \cite{vapnik1998} and ensemble learning \cite{breiman1998}. Furthermore supervised learning can be categorised into offline or batch learning and online learning (see section \ref{sec:batch} and \ref{sec:online}). 
\item[unsupervised learning] also known as clustering \cite{ben2005}. In this type of learning no labels are given and the system has to find a structure on its own, discovering hidden patterns in data.
\item[reinforcement learning] is the problem faced by an agent that must learn 
through trial-and-error interactions with a dynamic environment. It is based on programming agents by reward and punishment without needing to specify how the task is to be achieved \cite{sutton1998}.
\end{description}

All three types of problems can be viewed as optimization problems. The ML core task is to define a learning criterion, i.e the function to be optimized.

\section{Batch learning} \label{sec:batch}

@@

\section{Online learning} \label{sec:online}

>>>>

There are three types of ML classified depending on the nature of the learning input or output available to a learning system.
\begin{description}
\item[supervised learning]  the input data is a tuple which contains the example input and its desired outputs (also called labels). The list of tuples is called the training set. The concept of supervised learning comes from the supervisor, acting as a teacher in the learning process. The goal is to learn a general rule that maps inputs to outputs optimising a target function. There are two related problem types in supervised learning: classification and regression problems \cite{bishop2006}. Its two mainstream approaches are: support vector machines (SVMs) \cite{vapnik1998} and ensemble learning \cite{breiman1998}. Furthermore supervised learning can be categorised into offline or batch learning and online learning (see section \ref{sec:onoffline}). 
\item[unsupervised learning] also known as clustering \cite{ben2005}. In this type of learning no labels are given and the system has to find a structure on its own, discovering hidden patterns in data.
\item[reinforcement learning] is the problem faced by an agent that must learn 
through trial-and-error interactions with a dynamic environment. It is based on programming agents by reward and punishment without needing to specify how the task is to be achieved \cite{sutton1998}.
\end{description}

\section{Statistical learning theory} \label{sec:mltheory}

All ML problems can be viewed as optimisation problems. The ML core task is to define a learning criterion, i.e the function to be optimised.

In this thesis we will emphasised the supervised learning problem since it is the most common way of modelling financial problems.

Supervised learning consists in to find a learning function $f: X \rightarrow Y$ which models a set of examples called training set $S$ which have been drawn randomly and independently according to a unknown joint distribution function $p(x,y)$ on $X \times Y$:

$$
S= \{(x_1,y_1),\,(x_2,y_2),\dots\,,\,(x_n,y_n)\} \in \mathcal{S}, (x_i,y_i) \in X\times Y \quad \forall i = 1\dots n
$$

\noindent where $X \subseteq \mathbb{R}^m$ and $Y = \mathbb{R}$ in case of regression problems and $Y = \{1,-1\}$  if it is a classification problem.

A learning algorithm $\mathcal{A}$ takes as input a data set $S \in \mathcal{S}$ and output a function $f_S$:

\begin{eqnarray*}
\mathcal{A}: \mathcal{S} &\rightarrow & \mathcal{H} \\
S &\rightarrow &\mathcal{A}(S) = f_S
\end{eqnarray*}

\section{Batch and Online learning} \label{sec:onoffline}

@@
